``FISTA'' in Banach spaces with adaptive discretisations

### 2021-09-24 response.tex

	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity. The point of Figure 2 (and 3) is to demonstrate the accuracy of our theoretical rate predictions. While the initial rate of convergence is faster for the nonadaptive schemes, Figure 4 confirms that this does not translate to a large practical improvement.
\end{enumerate}

\section{Detailed response to second reviewer}
We are very sorry that you found our manuscript so difficult to read. You were right, the former foundations were not rigorous enough. We have rewritten these sections in line with your suggestion of removing the emphasis on the Banach space. The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space. Consequently, we also realised that the orthogonal projection was not needed at all, and we now allow $U^n$ to be subsets of $\F H$ rather than subspaces. The Banach space setting is reserved for examples discussed in Sections 5 to 7.

\begin{enumerate}
	\item \review{The main criticism is on section 2: In this section, there are no assumptions that relate $U$ and $H$. If $U=\bar{H}$ (closure in the norm of $U$?) like on page 1, then $H\subset U$, the subspaces $U_n$ are all subspaces of $H$, and $\Pi_n$ is the Riesz isomorphism on $U_n$, which should be the orthogonal projection of the the Riesz isomorphism on $H$ onto $U_n$. Here it is necessary that $U_n$ is a closed subspace.}

	As suggested, we now state that $\F U^n$ are closed in (10) and re-referenced throughout the document. The mention of $\F U$ on page 1 is now just a reference to the Lasso example introduced in a later section.

@@

	\item \review{I wonder, where in the paper the choice of the Banach space $U$ or the properties of $u^*$ matter. I have the impression that the results are all valid, if $U$ is removed from the paper and $E_0$ is defined as $E_0(u)=E(u)-\inf_{v\in H}E(v)$. Then the resulting algorithm tries to compute the infimum of $E$ on $H$ (which might not be attained).}

	Thank you for the suggestion. As previously mentioned, the main introduction of $\F U$ is now postponed to around Section 5.

	\item \review{The line (p2, l 54) defining $\Pi_n$ looks strange: the pairings $\langle\cdot,\cdot\rangle$ cannot both denote the inner product on $H$ as $u\in U_n^*$ might not be in $H$}

	As commented before, we define $\Pi_n$ on $\F H$ to remove any ambiguity.

@@

	\item \review{p.3: in what topology do you want to consider the closure of $U_n^*$? Why is that necessary at all?}

	As commented before, we define $\Pi_n$ on $\F H$ instead of $\F U_n^*$.

	\item \review{These definitions clash in the proof of Lemma 1 (Thm 6): There $w\in U_n+U_{n-1}$ has to be mapped into $U_n^*$ to be able to apply Lemma 2. This happens by means of an unnamed mapping, lets call it $M$, with the property $\Pi_nMw=w$. Again it is not clear whether this mapping exists (under the very abstract setting without any relation between $U$, $H$ and $U_n$, $U_{n-1}$. I think the claimed inequality (68) is wrong if $U_{n-1}$ is not a subspace of $U_n$, as in that case some projections of $u_{n-1}$ onto $U_n$ have to appear in (68).}

	Lemma 1 has now been modified to have $w\in \F U^n$. Equation (10) also has the assumption $u_{n-1}\in \F U^n$, instead of the suggested $\F U^{n-1}\subset \F U^n$.

### 2021-09-26 paper.tex
Generalised from Lasso to L1 reconstruction

	\begin{abstract}
		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever \edit{the optimisation domain}{a minimiser} is contained in a suitable Hilbert space. We propose a modified algorithm where each iteration is performed in a \edit{subspace, and that subspace is allowed to change at every iteration}{subset which is allowed to change at every iteration}. \edit{Analytically, this allows us to guarantee convergence in a Banach space setting}{Sufficient conditions are provided for guaranteed convergence}, although at a reduced rate depending on the conditioning of the specific problem. \edit{Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.}{These conditions have a natural interpretation when a minimiser exists in an underlying Banach space. A typical example is the Lasso problem where we provide detailed theoretical and numerical analysis.}
	\end{abstract}
	\keywords{Convex optimization \and Multiscale \and Multigrid \and Sparsity \and Lasso}

@@

	The contribution of this work is a modified FISTA algorithm which achieves two key properties:
	\begin{itemize}
		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved. For example, in Lasso discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}. The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
		\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$. With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence. In the Hilbert space setting this is the original $n^{-2}$ rate. In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
	\end{itemize}
	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty. Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}. Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}. This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations. The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$. The permitted refinement steps are also more broad in our work.

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{General examples}\label{sec: general examples}
	\edit{In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, Algorithm~\ref{alg: refining FISTA} is much more broadly applicable. Here we justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ can be easily computed in many examples.
	The cases where $\spcf0$ is finite or countable dimensional are quite straight forward. If the total number of refinements is finite (i.e. $\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_{\Varf0} = 1$. This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}. The examples considered here have $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ where $\{\tilde{\spcf0}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces. We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$. }{
	We consider the main use of Algorithm~\ref{alg: refining FISTA} to be where there exists a Banach space $(\spcf0,\Norm\cdot)$ such that $\spcf0\supset\F H$ and
	$$\inf_{\varf0\in\F H} \op{E}(\varf0) = \min_{\varf0\in\spcf0}\op{E}(\varf0) = \op{E}(\varf0^*)$$
	for some $\varf0^*\in\spcf0$. The cases where $\F H$ has finite or countable dimension are quite straightforward. If the total number of refinements is finite (i.e. $\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$), then $\vars3_{\Varf0} = 1$. This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}. In this section we give explicit computations of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $(\tilde{\spcf0}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
	}

@@

	\section{Lasso minimisation}\label{sec: Lasso definition}
	We now focus on the specific example of Lasso which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}. We consider three forms of Lasso which will be referred to as continuous, countable, and discrete Lasso depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively. In each case, the energy can be written as 
	\begin{equation}\label{eq: Lasso energy}
		\op{E}(\varf0) = \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\Norm{\varf0}
	\end{equation}
	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$. \edit{}{In the continuous-space case, we require $\A^*\colon\R^m\to C(\Domain)$. }Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing. Therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &=  \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2 + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&\leq \tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2
		\\&= \ip{[\tfrac12\A(\varf2+\varf0)-\data]}{\A(\varf2-\varf0)}
		\\&\leq \max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})\norm{\A(\varf2-\varf0)}_{\ell^2}
		\\&\leq \sqrt{2\max(\op{E}(\varf2), \op{E}(\varf0))}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{This norm further simplifies with
	\begin{align}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 &= \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\\&\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\&\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{align}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}|\A^*|_{\ell^2\to C^1}\Norm{\varf0^*}.
		\end{equation}}

@@

	For countable Lasso we consider discretisation subspaces of the form 
	$$\tilde{\spcf0}^k = \{\varf0\in \ell^1(\R) \st i\notin J_k\implies \varf0_i=0\}$$ for some sets $J_k\subset\F N$, i.e. infinite vectors with finitely many non-zeros. The key change in analysis from the continuous case is $\norm{\varf0^*}<\infty$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$. The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.

@@

	\subsubsection{Bounds for discretised functionals}\label{sec: bound discrete}
	We start by computing estimates for discretised Lasso. This covers the cases when either continuous/countable Lasso is projected onto $\spcf0^n$, or $\spcf0$ is finite dimensional. For notation we will use the continuous case, to recover the other cases just replace continuous indexing with discrete (i.e. $\varf0(\vvarx0) \leadsto \varf0_i$).

	Let $\tens{\Pi}_n\colon\F H\to\spcf0^n$ denote the orthogonal projection. For Lasso, the discretised function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$ is equivalent to replacing $\varf0$ with $\tens{\Pi}_n\varf0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.

	\paragraph{Discrete gradient}
	We can use $\tens{\Pi}_n$ to compute the discrete subdifferential at $\varf0_n\in\spcf0^n$:
	\begin{align}
		\partial_n \op{E}(\tens{\Pi}_n\varf0_n)(\vvarx0) &= [\tens{\Pi}_n\A^*(\A\varf0_n-\data)](\vvarx0) + \begin{cases}
			\{+\mu\} & \varf0_n(\vvarx0)>0 \\ [-\mu,\mu] & \varf0_n(\vvarx0)=0 
			\\\{-\mu\} & \varf0_n(\vvarx0)<0 
		\end{cases} 
		\\&\eqqcolon [\tens{\Pi}_n\A^*(\A\varf0_n-\data)](\vvarx0) + \mu\tens{\Pi}_n\sign(\varf0_n(\vvarx0))
	\end{align}
	where we define $s+\mu[-1,1] = [s-\mu,s+\mu]$ for all $s\in\R$, $\mu\geq0$.

	As $\Norm\cdot = \norm\cdot_1$, the natural metric for $\partial_n\op{E}$ is $\Norm\cdot_* = \norm\cdot_\infty$ which we can estimate
	\begin{align}
		\Norm{\partial_n \op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
		\\&= \max_{\vvarx0\in\Domain}\begin{cases}
			|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
			\\|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
			\\\max\left(|[\tens{\Pi}_n\A^*(\A\varf0_n-\data)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
		\end{cases}
	\end{align}
	which can be used directly in Lemma~\ref{thm: practical refinement criteria}.

>>>>

	\begin{abstract}
		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever \edit{the optimisation domain}{a minimiser} is contained in a suitable Hilbert space. We propose a modified algorithm where each iteration is performed in a \edit{subspace, and that subspace is allowed to change at every iteration}{subset which is allowed to change at every iteration}. \edit{Analytically, this allows us to guarantee convergence in a Banach space setting}{Sufficient conditions are provided for guaranteed convergence}, although at a reduced rate depending on the conditioning of the specific problem. \edit{Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.}{These conditions have a natural interpretation when a minimiser exists in an underlying Banach space. Typical examples are L1-penalised reconstructions where we provide detailed theoretical and numerical analysis.}
	\end{abstract}
	\keywords{Convex optimization \and Multiscale \and Multigrid \and Sparsity \and Lasso}

@@

	The contribution of this work is a modified FISTA algorithm which achieves two key properties:
	\begin{itemize}
		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved. For example, in \edit{Lasso}{L1 penalised reconstructions} discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}. The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
		\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$. With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence. In the Hilbert space setting this is the original $n^{-2}$ rate. In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
	\end{itemize}
	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty. Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}. Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}. This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations. The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$. The permitted refinement steps are also more broad in our work.

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{General examples}\label{sec: general examples}
	\edit{In this work we consider the Lasso problem to be both a motivating example and source of numerical examples, however, Algorithm~\ref{alg: refining FISTA} is much more broadly applicable. Here we justify this claim by demonstrating that the constants $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ can be easily computed in many examples.
	The cases where $\spcf0$ is finite or countable dimensional are quite straight forward. If the total number of refinements is finite (i.e. $\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$) then $\vars3_{\Varf0} = 1$. This holds for most finite dimensional problems as well as the countable Lasso example discussed in detail in Section~\ref{sec: Lasso definition}. The examples considered here have $\F H = L^2(\Domain)$ for some compact domain $\Domain\subset\R^d$ where $\{\tilde{\spcf0}^n\st n\in\F N\}$ are finite dimensional finite-element--like spaces. We will now clarify exactly what is meant by these properties and then demonstrate that they are sufficient to find simple formulae for the values $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$. }{
	We consider the main use of Algorithm~\ref{alg: refining FISTA} to be where there exists a Banach space $(\spcf0,\Norm\cdot)$ such that $\spcf0\supset\F H$ and
	$$\inf_{\varf0\in\F H} \op{E}(\varf0) = \min_{\varf0\in\spcf0}\op{E}(\varf0) = \op{E}(\varf0^*)$$
	for some $\varf0^*\in\spcf0$. The cases where $\F H$ has finite or countable dimension are quite straightforward. If the total number of refinements is finite (i.e. $\spcf0^n = \spcf0^N$ for all $n\geq N$, some $N\in\F N$), then $\vars3_{\Varf0} = 1$. This holds for most finite dimensional problems as well as the countable example discussed in detail in Section~\ref{sec: Lasso definition}. In this section we give explicit computations of $\vars3_{\Varf0}$ and $\vars3_{\op{E}}$ in the setting where $\F H = L^2(\Domain)$ for some domain $\Domain\subset\R^d$ and the subsets $(\tilde{\spcf0}^n)_{n\in\F N}$ will be finite dimensional finite-element--like spaces, as defined below.
	}

@@

	\section{\edit{Lasso}{L1 penalised} minimisation}\label{sec: Lasso definition}
	We now focus on the specific example of \edit{Lasso}{L1 penalised optimisation} which will be used for numerical results in \edit{Sectoin}{Section}~\ref{sec: numerics}. We consider three forms \edit{of Lasso}{} which will be referred to as the continuous, countable, and discrete \edit{Lasso}{problem} depending on whether the space $\spcf0$ is $\C M([0,1]^d)$, $\ell^1(\R)$, or finite dimensional respectively. In each case, the energy can be written as 
	\begin{equation}\label{eq: Lasso energy}
		\op{E}(\varf0) = \edit{\tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf0-\data)} + \mu\Norm{\varf0}
	\end{equation}
	for some $\A\colon \spcf0\to\R^m$ and $\mu>0$, where $\Norm\cdot=\norm\cdot_1$. \edit{}{We assume $\op{f}\in C^1(\R^m)$ is convex with $\nabla\op{f}$ 1-Lipschitz and locally bounded, and in the continuous-space case, we require $\A^*\colon\R^m\to C(\Domain)$. }Let $\varf0^*\in\argmin_{\varf0\in\spcf0}\op{E}(\varf0)$.

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing. Therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&= \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
		\\&\lesssim_{\edit{}{\op{E}(\varf2)}} \edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{This norm further simplifies with
	\begin{multline}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{multline}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}|\A^*|_{\ell^2\to C^1}\Norm{\varf0^*}.
		\end{equation}}

@@

	For countable \edit{Lasso}{dimensions} we consider discretisation subspaces of the form 
	$$\tilde{\spcf0}^k = \{\varf0\in \ell^1(\R) \st i\notin J_k\implies \varf0_i=0\}$$ for some sets $J_k\subset\F N$, i.e. infinite vectors with finitely many non-zeros. The key change in analysis from the continuous case is $\norm{\varf0^*}<\infty$, which leads to $\vars3_{\Varf0}=1$ and the expected optimal rate of $n^{-2}$, independent of $\vars3_{\op{E}}$ or any additional properties of $\A$. The number of refinements will also be finite, therefore $n_k=\infty$ for some $k$ and the remaining conditions of Theorems~\ref{thm: exponential FISTA convergence} and~\ref{thm: stronger exponential FISTA convergence} hold trivially.

@@

	\subsubsection{Bounds for discretised functionals}\label{sec: bound discrete}
	We start by computing estimates for discretised \edit{Lasso}{energies}. This covers the cases when either the continuous/countable \edit{Lasso}{energy} is projected onto $\spcf0^n$, or $\spcf0$ is finite dimensional. For notation we will use the continuous case, to recover the other cases just replace continuous indexing with discrete (i.e. $\varf0(\vvarx0) \leadsto \varf0_i$).

	Let $\tens{\Pi}_n\colon\F H\to\spcf0^n$ denote the orthogonal projection. \edit{For Lasso}{In our case}, the discretised function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$ is equivalent to replacing $\varf0$ with $\tens{\Pi}_n\varf0$, and $\A^*$ with $\tens{\Pi}_n\A^*$.

	\paragraph{Discrete gradient}
	We can use $\tens{\Pi}_n$ to compute the discrete subdifferential at $\varf0_n\in\spcf0^n$:
	\begin{align}
		\partial_n \op{E}(\tens{\Pi}_n\varf0_n)(\vvarx0) &= [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)](\vvarx0) + \begin{cases}
			\{+\mu\} & \varf0_n(\vvarx0)>0 \\ [-\mu,\mu] & \varf0_n(\vvarx0)=0 
			\\\{-\mu\} & \varf0_n(\vvarx0)<0 
		\end{cases} 
		\\&\eqqcolon [\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)](\vvarx0) + \mu\tens{\Pi}_n\sign(\varf0_n(\vvarx0))
	\end{align}
	where we define $s+\mu[-1,1] = [s-\mu,s+\mu]$ for all $s\in\R$, $\mu\geq0$.

	As $\Norm\cdot = \norm\cdot_1$, the natural metric for $\partial_n\op{E}$ is $\Norm\cdot_* = \norm\cdot_\infty$ which we can estimate
	\begin{align}
		\Norm{\partial_n \op{E}(\varf0_n)}_* &= \max_{\vvarx0\in\Domain}\min\left\{|\varf1| \st \varf1\in \tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) +  \mu\sign(\varf0_n(\vvarx0))\right\}
		\\&= \max_{\vvarx0\in\Domain}\begin{cases}
			|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) + \mu| & \varf0_n(\vvarx0)>0
			\\|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0) - \mu| & \varf0_n(\vvarx0)<0
			\\\max\left(|[\tens{\Pi}_n\A^*\edit{}{\nabla\op{f}}(\A\varf0_n-\data)(\vvarx0)| - \mu, 0\right) & \varf0_n(\vvarx0) = 0
		\end{cases}
	\end{align}
	which can be used directly in Lemma~\ref{thm: practical refinement criteria}.
